Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data

### 2017-01-05 Inelastic/analysis.tex
first sloppy version

few words, mainly a table summarizing uncertainties. Figure~\ref{fig:unc}.

>>>>

Uncertainties on the total prediction of background events arise from the relative uncertainties on the measure of the normalization 
factor $\tau_{bkg}$ and amount to 6\%, while uncertainties arising from radiogenic neutrons contributions are neglected. 
Uncretainty on the shape of the predicted bakground distribution are assesed by reporting the maximal discrepancy in the ROI between
the $^{60}$Co and $^{232}$Th calibration samples, according to this it is assigned to the expected yield of each subregion a 4\% uncertainty,
uncertainty belonging to different regions are considered independent from each other.
%It is important not only to describe correctly the expected total background but also its distribution

Signal model, Energy scale uncertainties.... Uncertainties related to energy scale and more generally to detector response 
are taken into account by relative uncertainties on the measure of $L_Y$,$\mathcal{L}_{eff}$,$Y$, $Q_Y$ and $\rho$. Has been shown 
by the simulation that these type of uncertainty affect the total signal yield in the ROI by less than a percent for a wide range of masses,
however they greatly affects the pdf of the signal model in the ROI. For each WIMP mass several signal simulation sample are produced 
warying these parameter respectively $\pm 1 \sigma$, for each region is computed an uncertainty by adding in quadrature the variations
%FIXME: explain this better, the up variation are separated from down variations and added togheter
with respect to nominal of each case, Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for WIMP mass of 100~GeV.

Uncertainty on the total yield of the signal arising from uncertainties on the selection acceptance are found to be very weakly dependent on 
the WIMP mass, an overall 6\% acceptance uncertainty is then applied to all WIMP hypotesis.

%FIXME: express this in an understandable way
All the uncertainties discussed here are threated as nuissance parameter in the likelihood, which are contrained by a gaussian distribution.

### 2017-01-05 Inelastic/results.tex
bkg model written
first sloppy version

\section{Results}
No evidence of dark matter.

>>>>

\section{Results}
In an exposure of 34~Kg per 224~days of liquid xenon a yield of 764 events are found in the region of interest,
which is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$. The distribution 
of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative
uncertainties.  
This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
and its asymptotic distributions described in \cite{asympt}. 90\% CL$_s$ \cite{cls} confidence level limits are 
computed on the spin dependent cross section as a function of the WIMP mass and shown in Figure~\ref{fig:limits}.
